---
title: "Data IO Connections with R"
author: "Office of Institutional Effectiveness"
output: html_document
runtime: shiny
resource_files:
- r/data_io_util.R
- sql/*
- misc/*
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE)
```

# {.tabset}

## Data IO Connections 

### Loading all libraries and functions needed
#### IMPORTANT: data_io_util.R file will need to be copied over to any separate project.
```{r server-side}
library(here)
source(here::here("r", "data_io_util.R"))
```

### Setting up keyring (Banner, Edify, and Pins)
#### Note how the service argument, in the call to key_set function, is changed for all separate credentials saved.
```{r keyring, eval=FALSE}
library(keyring)

### Banner
# for storing an individual's username
keyring::key_set(service="sis_db", username="username")
# for storing an individual's password
keyring::key_set(service="sis_db", username="password")

### Edify
# for storing an individual's username
keyring::key_set(service="edify", username="username")
# for storing an individual's password
keyring::key_set(service="edify", username="password")

### Pins
# for storing the API key for pins on RStudio Connect
keyring::key_set(service="pins", username="api_key")

```

### Pull data via prebuilt function (Banner, Edify, and Pins)
```{r prebuilt}
library(DT)
library(tidyverse)

### Banner
# Function assumes that "query.sql" is located in a folder called "sql".
df <- get_data_from_sql_file(file_name="query.sql",
                             dsn="REPT")
# display data pulled in table
DT::datatable(df, rownames=FALSE)

### Edify
# Function assumes that "edify_query.sql" is located in a folder called "sql".
df <- get_data_from_sql_file(file_name="edify_query.sql",
                             dsn="edify")
# display data pulled in table
DT::datatable(df, rownames=FALSE)

### Pins
# Function assumes that "edify_query.sql" is located in a folder called "sql".
df <- get_data_from_pin(pin_name="student_type_audit_student_type_determination_variables_pin") %>%
  # only a random sample of data displayed to improve load time
  sample_n(100)
# display data pulled in table
DT::datatable(df, 
              rownames=FALSE,
              # allow for horizontal scrolling, when width of data goes off page
              options=list( scrollX = TRUE ))


```


## Contents of data_io_util.R
```{r comment='', echo=FALSE}
r_content <- read_file( here::here("r", "data_io_util.R") )
```
```{r, code=r_content,eval=FALSE}
```


## Example DSN Entries

### Finding file locations with terminal
```{bash, eval=FALSE}
odbcinst -j
```
### File contents of odbcinst.ini
```{r comment='', echo=FALSE}
cat(readLines(here::here("misc", "example_odbcinst.ini")), sep = '\n')
```

### File contents of odbc.ini
```{r comment='', echo=FALSE}
cat(readLines(here::here("misc", "example_odbc.ini")), sep = '\n')
```


## Aditional Information

### For Windows Users (informational only)
#### Changing Oracle driver name:
Oracle in instantclient* is set by odbc_install.exe and can be altered if you change the registry:

1. In HKEY_LOCAL_MACHINE\SOFTWARE\ODBC\ODBCINST.INI\ODBC Drivers, change the name of "Oracle in instantclient*" to whatever you want.

2. Rename the, "Oracle in instantclient*" key in HKEY_LOCAL_MACHINE\SOFTWARE\ODBC\ODBCINST.INI to the same name you used above.

\
\
