---
title: "Project Documentation"
author: Office of Institutional Effectiveness
output: 
  html_document:
    theme: journal
    highlight: tango
    toc: true
    toc_depth: 4
    toc_float:
      collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE)
```

```{r code}
```

# Project Purpose
To make the IPEDS reporting process as easy and transparent as possible. All reports are now available at the click of a download button in the associated Shiny app.

## Data Sources
All data is currently being pulled from Edify. Original (older version) pulls directly from Banner.

## Intended Audience
IPEDS; the federal government

# Project Timeline
Project is complete, but can be improved.

## Steps to Submit Reports
1. Update data set
    a. Set the pull_data variable in pull.R to TRUE
    b. Either source pull.R or run Shiny app
    c. Set the pull_data variable back to FALSE to allow Shiny app to load faster
2. Run Shiny app
    a. Adjust selected terms  
    b. Click "Download Report" buttons 
3. Submit downloaded reports to IPEDS

## Due Dates
All report must be submitted, validated, and locked by the second Wednesday of February.

## Repetition Cycle
Yearly

## Maintainance
There may be changes to filter logic, or report formats from year to year.

## Future Development
1. Once program data is fixed in Banner, the data from dsc_programs_all should no longer be needed.