---
title: "USHE Faculty Workload"
author: "LaVoy"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Disable scientific notation when displaying numbers.
options(scipen=999)

library(utHelpR)
library(dplyr)
```

```{r}

faculty_sql_location <- "faculty_workload/faculty_term.sql"
faculty_df <- utHelpR::get_data_from_sql_file(faculty_sql_location, 
                                              dsn="REPT")

non_instructional_workload_sql_location <- "faculty_workload/faculty_term_non_instructional_workload.sql"
non_instructional_faculty_workload_df <- utHelpR::get_data_from_sql_file(non_instructional_workload_sql_location, 
                                                                         dsn="REPT") %>%
  dplyr::filter( term_code == '202240' )


instructional_workload_sql_location <- "faculty_workload/faculty_term_instructional_workload.sql"
instructional_faculty_workload_df <- utHelpR::get_data_from_sql_file(instructional_workload_sql_location, 
                                                                  dsn="REPT") %>%
  dplyr::filter( term_code == '202240' )


# Faculty FTE ( Census Count )
total_instructional_faculty <- dplyr::n_distinct(instructional_faculty_workload_df$sis_id)

# Faculty Instructional Workload ( Total Instructional Activity - All Levels )
total_faculty_contact_hours <- sum(instructional_faculty_workload_df$course_contact_hours)
total_instructional_credit_hours <- sum(instructional_faculty_workload_df$course_credit_hours)
total_student_credit_hours <- sum(instructional_faculty_workload_df$course_student_credit_hours)


# Part Time Instruction
# TODO: Need indicators for the following faculty classifications.
# 1. Regular Faculty Overload
# 2. Part Time Adjunct and Wage Rated Instructors
# 3. Teaching Assistants

```


#### Faculty FTE ( Census Count )
* **Total Institutional Instructional Faculty:** `r total_instructional_faculty`
   
#### Faculty Instructional Workload ( Total Instructional Activity - All Levels )
* **Total Faculty Contact Hours:** `r total_faculty_contact_hours`
* **Total Instructional Credit Hours:** `r total_instructional_credit_hours`
* **Total Student Credit Hours:** `r total_student_credit_hours`
        
#### Part Time Instruction
* Headcount of Part Time Instructors
    + **Regular Faculty Overload:**
    + **Part Time Adjunct and Wage Rated Instructors:**
    + **Teaching Assistants:**
    +    Total Part Time Instructors Headcount:
* Faculty Contact Hours per Part Time Instructors Headcount
    + **Regular Faculty Overload:**
    + **Part Time Adjunct and Wage Rated Instructors:**
    + **Teaching Assistants:**
    +    Total Faculty Contact Hours per Part Time Instructors Headcount:
* Instructional Credit Hours (ICH) Per Part Time Instructors Headcount
    + **Regular Faculty Overload:**
    + **Part Time Adjunct and Wage Rated Instructors:**
    + **Teaching Assistants:**
    +    Total Instructional Credit Hours (ICH) Per Part Time Instructors Headcount:
* Student Credit Hours (SCH) Per Part Time Instructors Headcount
    + **Regular Faculty Overload:**
    + **Part Time Adjunct and Wage Rated Instructors:**
    + **Teaching Assistants:**
    +    Total Student Credit Hours (SCH) Per Part Time Instructors Headcount:
* Percent of Institutional Student Credit Hours Generated by Part Time Instructors
    + Regular Faculty Overload:
    + Part Time Adjunct and Wage Rated Instructors:
    + Teaching Assistants:
    +    Total Percent of Institutional Student Credit Hours Generated by Part Time Instructors:
               
